Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-05 article.tex
Add weighted base filter

% Filtering methodology
Prior inferring the network, the fluorescent calcium time series are smoothed
using several linear and non linear filters. A low-pass filter, a high-pass
filter and a non linear hard-thresholding based filter are
applied for each possible time step $t$
\begin{align}
X^\prime_{t,i} &= \sum_{l=-3}^2 a_l X_{t+l,i} \forall i, \\
X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
\end{align}
where the $a_l$ coefficients were taken in one of the four following tuples
$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
$(\left\{a_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
$(\left\{a_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
$(\left\{a_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is the minimal
fluorescence signal .

Then we apply a non-linear filter based on the current
activity of the systems in order to favour the association measure when
directly connected neurons are firing together, while artificially
reducing the association measure in case of extreme network activity,
i.e. high when a network firing is happening and low when no neuron is
active.

@@

\begin{table}[h!]
\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & & \\ \hline
2 & Pre-processing & & & &\\ \hline
3 & PCA & & & &  \\ \hline
4 & Weighting & & & &  \\ \hline
5 & Averaging & & & &  \\ \hline

@@

\begin{table}[h!]
\begin{tabular}{|c|c||c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & &\\ \hline
2 & Correlation & & & &\\ \hline
3 & GENIE3 & & & & \\ \hline
4 & GTE & & & & \\ \hline

>>>>

% Filtering methodology
Prior inferring the network, the fluorescent calcium time series are smoothed
using several linear and non linear filters. A low-pass filter, a high-pass
filter and a non linear hard-thresholding based filter are
applied for each possible time step $t$
\begin{align}
X^\prime_{t,i} &= \sum_{l=-3}^2 c_l X_{t+l,i} \forall i, \\
X^{\prime\prime}_{t,i} &= X^{\prime}_{t,i} - X^{\prime}_{t-1,i} \forall i, \\
X^{\prime\prime\prime}_{t,i} &= {X^{\prime\prime}_{t,i}}^{0.9} I(X^{\prime\prime}_{t,i} \geq f_3) \forall i,
\end{align}
where the $c_l$ coefficients were taken in one of the four following tuples
$(\left\{c_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 1)$,
$(\left\{c_l\right\}_{l=-3}^2)=(0, 0, 1, 1, 1, 0)$,
$(\left\{c_l\right\}_{l=-3}^2)=(1, 1, 1, 1, 0, 0)$ or
$(\left\{c_l\right\}_{l=-3}^2)=(0.4, 0.8, 1, 1, 0, 0)$ and $f_3$ is a parameter
of the hard-threshold filter.

Then we apply a non-linear filter based on the current
activity of the systems in order to favor the association measure when
a medium size set of neurons are firing together, while artificially
reducing the association measure in case of extreme network activity,
i.e. high when a network firing is happening and low when no neuron is
active:
\begin{align}
a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
                   \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
X^{\prime\prime\prime\prime}_{t,i} &=
\left\{
  \begin{array}{l}
    1  : r_t < 0\\
    {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
  \end{array}
\right.
\end{align}
where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
parameters $b_1, b_2, b_3, f_4, f_5, f_6$.

% TODO speak about why averaging

@@

\begin{table}[htb]
\centering
\begin{tabular}{|c|c||c|c|c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & & \\ \hline
2 & Pre-processing & & & &\\ \hline
3 & PCA & & & &  \\ \hline
4 & Weighting & & & &  \\ \hline
5 & Averaging & & & &  \\ \hline

@@

\begin{table}[htb]
\centering
\begin{tabular}{|c|c||c|c|c|c|} \hline
\# & Stage & normal-1 & normal-2 & normal-3 & normal-4 \\ \hline
1 & Inverse correlation & & & &\\ \hline
2 & Correlation & & & &\\ \hline
3 & GENIE3 & & & & \\ \hline
4 & GTE & & & & \\ \hline
